Parsing Postfix log files

### 2009-02-26 doc/logparser-introduction.tex
Cite my paper - it needs to be added to the bibliography. Change section to chapter.

\vspace{1em}\noindent\textbf{Layout:}

@@

Section~\ref{background} provides background information useful in
understanding the thesis, parser, and architecture.

Section~\ref{state of the art review} reviews both the previously published
research in this area and other available Postfix log file parsers,
discussing why they were deemed unsuitable for the task, including why they
could not be improved or expanded upon.

@@

Section~\ref{rules in architecture} discusses the parsing rules in detail,
explaining the purpose and usage of each field in a rule, referring to an
example rule and sample data it matches successfully against.  The pros and
cons of overlapping rules are considered, including techniques for
detecting unintentional overlaps.  Rule efficiency concerns are discussed,
in particular the optimisations used by the algorithm.  The section
concludes with a description of using the tools provided with the parser to
generate new rules (specifically the regex in each rule) from unparsed log
lines.

Section~\ref{Postfix Parser Implementation} contains the core of the paper,
describing a naive parsing algorithm and the complications initially
encountered that shaped the full algorithm.  A flow chart and a discussion
of the emergent behaviour exhibited by the algorithm accompanies a
comprehensive explanation of the different stages of the initial algorithm.
The framework that actions and rules fit into is documented, then the
actions taken during execution of the algorithm are described, followed by
the process of adding a new action.  The section concludes with an in-depth
description of the further complications discovered, and their solutions
that complete the parser.

Section~\ref{parsing coverage} analyses the coverage the parser achieves
over a set of \numberOFlogFILES{} log files taken from a mail server
handling mail for over 700 users, averaging 8500 mails per day
(\graphref{Mails received per day}).  Coverage is described both
in terms of the fraction of log lines parsed and the fraction of mails and
connections successfully reconstructed by the parsing algorithm; dealing
with false negatives and a discussion of the difficulties in identifying
false positives is also included.  As part of determining the coverage of
the parser a random sampling of log lines was parsed, and the correctness
of the results manually verified.

Section~\ref{limitations and improvements in implementation} lists the
limitations of the algorithm, then suggests some ways of dealing with them,
with the goal of improving parsing and reproduction of the journey a mail
takes through Postfix.

Section~\ref{conclusion} contains the conclusion of the thesis, describing
the results of the research, design, and implementation of the parser.

@@

>>>>

\section{Thesis Layout}

@@

Chapter~\ref{background} provides background information useful in
understanding the thesis, parser, and architecture.

Chapter~\ref{state of the art review} reviews both the previously published
research in this area and other available Postfix log file parsers,
discussing why they were deemed unsuitable for the task, including why they
could not be improved or expanded upon.

@@

Chapter~\ref{rules in architecture} discusses the parsing rules in detail,
explaining the purpose and usage of each field in a rule, referring to an
example rule and sample data it matches successfully against.  The pros and
cons of overlapping rules are considered, including techniques for
detecting unintentional overlaps.  Rule efficiency concerns are discussed,
in particular the optimisations used by the algorithm.  The section
concludes with a description of using the tools provided with the parser to
generate new rules (specifically the regex in each rule) from unparsed log
lines.

Chapter~\ref{Postfix Parser Implementation} contains the core of the paper,
describing a naive parsing algorithm and the complications initially
encountered that shaped the full algorithm.  A flow chart and a discussion
of the emergent behaviour exhibited by the algorithm accompanies a
comprehensive explanation of the different stages of the initial algorithm.
The framework that actions and rules fit into is documented, then the
actions taken during execution of the algorithm are described, followed by
the process of adding a new action.  The section concludes with an in-depth
description of the further complications discovered, and their solutions
that complete the parser.

Chapter~\ref{parsing coverage} analyses the coverage the parser achieves
over a set of \numberOFlogFILES{} log files taken from a mail server
handling mail for over 700 users, averaging 8500 mails per day
(\graphref{Mails received per day}).  Coverage is described both
in terms of the fraction of log lines parsed and the fraction of mails and
connections successfully reconstructed by the parsing algorithm; dealing
with false negatives and a discussion of the difficulties in identifying
false positives is also included.  As part of determining the coverage of
the parser a random sampling of log lines was parsed, and the correctness
of the results manually verified.

Chapter~\ref{limitations and improvements in implementation} lists the
limitations of the algorithm, then suggests some ways of dealing with them,
with the goal of improving parsing and reproduction of the journey a mail
takes through Postfix.

Chapter~\ref{conclusion} contains the conclusion of the thesis, describing
the results of the research, design, and implementation of the parser.

@@

\section{XXX NOTES}

Portions of \sectionref{parser architecture}, \sectionref{Postfix Parser
Implementation}, and \sectionref{Results} have previously been published at
a conference~\cite{sgai-2008}, and later reprinted in a
journal~\cite{elsevier-2009}.  Publication of the conference paper and
journal article above was supported by Science Foundation Ireland
RFP~05/RF/CMS002.
